\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-13 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
changement lise partie theorique

\begin{table}[htbp]
  \centering
  \caption{Trade cost reduction: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c||c|c}
\hline
Mode & \multicolumn{2}{|c||}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
& (A) & (B) & (C) & (D)  \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-6.4 &-6.4   \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&-6.4&	-3.1	 \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-3.3 \\ \hline \hline
\multicolumn{4}{l}{(1) Lower fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 	\textbf{2.50}	&\textbf{3.16}	&	\textbf{3.63}&	\textbf{4.26 }  \\\hline
Variety effect (\%)&1.36 &0.48	&-0.43	&-1.28 \\
Price effect (\%)&	1.14 &	2.66&		 4.08&	5.63 \\ \hline \hline
\multicolumn{4}{l}{(2) Constant fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.23&	2.18 & 2.39	&3.38 	 \\ \hline
Variety effect (\%)& -0.83 	&-1.32	&-2.60	& -3.12 \\
Price effect (\%)&2.08 &3.56	&5.20	& 6.83  \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In Columns B and D, we first simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

\textbf{Inverser panel 1 et 2 pour avoir le même ordre dans le tableau et le texte xxxxGD}
In line with the literature, we find that a reduction of trade costs  induces welfare gains
% whatever the transport mode (and the associated magnitude of the transport costs decrease).
The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction.
Welfare gains are higher when the trade cost reduction includes a decrease in additive trade costs.
This is consistent with the analytical results of \cite{sorensen2014} and the quantitative ones of \cite{Irrazabal_2015}.
%in a different exercise of trade cost reduction though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade cost reduction. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.}
Quantitatively, the welfare gains are sizeable. In our preferred scenario, the reduction in variable transport costs generates a relative welfare gain higher by around 25\% percentage point when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in ad-valorem costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). xxxGD ajuster avec les nouveaux chiffresxxx.
%Closely related to our work, \cite{Irrazabal_2015} also quantify the welfare losses of imposing trade taxes depending on whether they are additive or ad-valorem. If we share a similar conclusion regarding the importance of additive costs, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem).
\smallskip

@@

\paragraph{Holding fixed costs constant} To understand the changes induced by the additive costs, we start by considering the scenario with a constant fixed export cost (Table  \ref{tab:resultats_modele}, Panel (2)). In this case, the welfare changes are solely attributable to the reduction in the variable transport costs, and the difference of results stems from whether transport cost involves an additive part or not.

Consider first the benchmark model \textit{\`{a} la} M\'{e}litz with only ad-valorem costs (Table \ref{tab:resultats_modele}, Panel (2), Columns (A) and (C)).
The reduction in the ad-valorem cost induces a negative variety effect, which is yet more than counteracted by a positive price effect.
With the reduction in $\tau$, the expected average export profit increases and more firms can now export.
More exporting firms means more competition in each domestic market.
A well known result is that this raises the productivity threshold to enter the domestic markets.
Accordingly, the number of domestic active firms is reduced, even if a larger number of them is able to export.
As a whole, the total number of varieties accessible to the consumer is reduced in some of the cases we study here.
This reduces welfare everything else equal.
This detrimental effect is counteracted by a positive price competitiveness effect.
Due to the tougher selection on the domestic market, the less productive firms no longer enter.
As a result, the average productivity on the domestic market increases, which pushes the average productivity upwards.
As reported in Table \ref{tab:resultats_modele}, the strength of the price competitiveness effect dominates, inducing positive welfare from the reduction in ad-valorem costs, consistently with the analytical results of \cite{melitz}.

The situation changes when the reduction in international transport costs also occurs through the reduction in an additive component.
As reported in Table \ref{tab:resultats_modele}, panel (2), columns (B) and (D), the welfare gains are stronger than in the pure ad-valorem case; and this is driven by a more positive price competitiveness effect and despite the more negative variety effect (comparing with Columns (A) and (C), same panel).
This can be accounted for as follows.

@@

\paragraph{Taking into account the reduction in fixed costs}As mentioned above, our preferred scenario includes, in addition to the reduction of variable costs, a reduction in fixed export costs, based on \cite{Lincoln_McCallum2018}’s empirical evidence.
The associated welfare gains are reported in Table \ref{tab:resultats_modele}, Panel (1).
Two results emerge.
First, the welfare gains induced by the trade cost reduction are stronger in magnitude.
While this is not a surprising result \textit{per se} (we now consider two sources of internation frictions: fixed and variable costs)), this exercise delivers also a quantification of the welfare gains associated with a reduction in the fixed export cost: They are substantial and amount to between 0.6 to 1.25 percentage point depending on the transport mode.
\textbf{passer en \% GD xxxxx}
This can be accounted for as follows.
The reduction in the fixed export cost pushes more firms to export.
This increases the number of available imported varieties for the consumer, which counteracts the reduction in the number of domestic varieties induced by the tougher selection on the domestic market.
As a result, the joined reduction in variable costs and in $f_x$ lead to a less negative variety effect (which even turns out to be positive in the scenario with only ad-valorem costs).
This, combined with a positive price competitiveness effect, accounts for the stronger welfare gains reported in Panel (2).
 \textbf{panel 1 ou 2 ? Voir plus haut GD xxxxx}.

Second, the main message of the paper remains valid.
The welfare gains of the trade cost reduction are still higher when part of this structural change is achieved through a reduction in additive transport costs, by the same order of magnitude (around + 1.2 percentage points) \textbf{passer en \% GD xxxxx}.
Put differently, the balance between the effect of the reduction of additive costs and the reduction of ad-valorem costs does does not seem to depend on reduction of fixed costs. In the end, the welfare gains are the highest when trade cost reduction induces a combined reduction in both variable and fixed export costs, and when (part of) the reduction in the variable part is achieved through a decrease in the additive component, as observed empirically.\smallskip

In line with \cite{sorensen2014} and \cite{Irrazabal_2015}, our overall theoretical results show the importance of taking into account the additive components of international trade costs.
Additive costs have a substantial impact effect on the composition of the baskets of exported goods.
This, in turn, has important consequences for welfare.
Relying on our empirical estimates of transport costs over 1974-2019, we obtain that the 3.4\% reduction of variable costs in Air transport, combined with the reduction in the fixed export costs, has induced an 3.16\% increase in welfare, much higher than if only ad-valorem costs were modeled (2.5\%).
\textbf{passer en \% GD xxxxx}.
We find a similar result in vessel transport with the observed 6.4\% in total variable costs along with the reduction in the fixed export costs.
The relative increase in welfare is 4.3\% (as compared to 3.6\% in a pure ad-valorem world).
Neglecting the existence and long-term evolution additive costs thus leads to a substantial underestimation of the welfare gains of trade cost reduction.

>>>>

\begin{table}[htbp]
  \centering
  \caption{Trade cost reduction: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c||c|c}
\hline \hline
Mode & \multicolumn{2}{|c||}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
& (A) & (B) & (C) & (D)  \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.73 &-3.73 &-4.9 &-4.9   \\
$\Delta \tau$ (in pp) & -3.73	&-1.95&-4.9&	-3.53	 \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-1.84&	0&	-1.36 \\ \hline \hline
\multicolumn{4}{l}{(1) Constant fixed export cost} \\ \hline
$\Delta \beta$ (in pp) & 0&	-15.4 & 0	&+9.3 	 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.38&	2.46 & 1.71	&2.20 	 \\ \hline
Variety effect (\%)& -0.92 	&-2.57	&-1.09	& -1.87 \\
Price effect (\%)&2.34 &5.24	&2.85	& 4.19  \\ \hline
\multicolumn{4}{l}{(2) Lower fixed export cost} \\ \hline
$\Delta \beta$ (in pp) & 0&	-15.2 & 0	&+9.2 	 \\
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 	\textbf{2.62}	&\textbf{3.66}	&	\textbf{2.83}&	\textbf{3.23 }  \\\hline
Variety effect (\%)&1.20 &-0.45	&0.92	&0.23 \\
Price effect (\%)&	1.42 &	4.14&		1.90&	3.00 \\ \hline \hline
\end{tabular}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In Columns B and D, we first simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

In line with the literature, we find that a reduction of trade costs  induces welfare gains
% whatever the transport mode (and the associated magnitude of the transport costs decrease).
The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction.
Welfare gains are higher when the trade cost reduction includes a decrease in additive trade costs.
This is consistent with the analytical results of \cite{sorensen2014} and the quantitative ones of \cite{Irrazabal_2015}.
%in a different exercise of trade cost reduction though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade cost reduction. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.}
Quantitatively, the welfare gains are sizeable. In our preferred scenario, the reduction in variable transport costs generates a relative welfare gain higher by around 40\% (14\%) in air (vessel) transport when such a reduction partly occurs through the additive component, rather than when it realizes through a decrease in ad-valorem costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). One can also notice that the welfare gains are much larger when the trade cost reduction is achieved through a larger reduction in the additive component (such that $\beta$ reduces, as for air transport, Columns (B) vs (A)) than when it mostly occurs through the ad-valorem component (in which case $\beta$ increases, as for vessel transport, Columns (D) vs (C)).
%Closely related to our work, \cite{Irrazabal_2015} also quantify the welfare losses of imposing trade taxes depending on whether they are additive or ad-valorem. If we share a similar conclusion regarding the importance of additive costs, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem).
\smallskip

@@

\paragraph{Holding fixed costs constant} To understand the changes induced by the additive costs, we start by considering the scenario with a constant fixed export cost (Table  \ref{tab:resultats_modele}, Panel (1)). In this case, the welfare changes are solely attributable to the reduction in the variable transport costs, and the difference of results stems from whether transport cost involves an additive part or not.

Consider first the benchmark model \textit{\`{a} la} M\'{e}litz with only ad-valorem costs (Table \ref{tab:resultats_modele}, Panel (1), Columns (A) and (C)).
The reduction in the ad-valorem cost induces a negative variety effect, which is yet more than counteracted by a positive price effect.
With the reduction in $\tau$, the expected average export profit increases and more firms can now export.
More exporting firms means more competition in each domestic market.
A well known result is that this raises the productivity threshold to enter the domestic markets.
Accordingly, the number of domestic active firms is reduced, even if a larger number of them is able to export.
As a whole, the total number of varieties accessible to the consumer is reduced in some of the cases we study here.
This reduces welfare everything else equal.
This detrimental effect is counteracted by a positive price competitiveness effect.
Due to the tougher selection on the domestic market, the less productive firms no longer enter.
As a result, the average productivity on the domestic market increases, which pushes the average productivity upwards.
As reported in Table \ref{tab:resultats_modele}, the strength of the price competitiveness effect dominates, inducing positive welfare from the reduction in ad-valorem costs, consistently with the analytical results of \cite{melitz}.

The situation changes when the reduction in international transport costs also occurs through the reduction in an additive component.
As reported in Table \ref{tab:resultats_modele}, Panel (1), columns (B) and (D), the welfare gains are stronger than in the pure ad-valorem case; and this is driven by a more positive price competitiveness effect and despite the more negative variety effect (comparing with Columns (A) and (C), same panel).
This can be accounted for as follows.

@@

\paragraph{Taking into account the reduction in fixed costs} As mentioned above, our preferred scenario includes, in addition to the reduction of variable costs, a reduction in fixed export costs, based on \cite{Lincoln_McCallum2018}’s empirical evidence.
The associated welfare gains are reported in Table \ref{tab:resultats_modele}, Panel (2).
Two results emerge.
First, the welfare gains induced by the trade cost reduction are stronger in magnitude.
While this is not a surprising result \textit{per se} (we now consider two sources of international frictions: fixed and variable costs)), this exercise delivers also a quantification of the welfare gains associated with a reduction in the fixed export cost: They are substantial, by inducing welfare gains higher by around 60-80\% depending on the transport mode.\footnote{For instance, consider the case of Air transport (Column (A)). The supplementary welfare gains associated with the reduction in $f_x$ is obtained as the ratio 2.62/1.38, i.e. 89\%. \textbf{xxx check calculus}} This can be accounted for as follows. The reduction in the fixed export cost pushes more firms to export.
This increases the number of available imported varieties for the consumer, which counteracts the reduction in the number of domestic varieties induced by the tougher selection on the domestic market.
As a result, the joined reduction in variable costs and in $f_x$ lead to a less negative variety effect (which may even turn out to be positive, e.g. in vessel transport). This, combined with a positive price competitiveness effect, accounts for the stronger welfare gains reported in Panel (2).

Second, the main message of the paper remains valid.
The welfare gains of the trade cost reduction are still higher when part of this structural change is achieved through a reduction in additive transport costs, even if lower in magnitude (around + 50\%). Put differently, the balance between the effect of the reduction of additive costs and the reduction of ad-valorem costs does not seem to depend on reduction of fixed costs. In the end, the welfare gains are the highest when trade cost reduction induces a combined reduction in both variable and fixed export costs, and when (part of) the reduction in the variable part is achieved through a decrease in the additive component, as observed empirically.\smallskip

In line with \cite{sorensen2014} and \cite{Irrazabal_2015}, our overall theoretical results show the importance of taking into account the additive components of international trade costs.
Additive costs have a substantial impact effect on the composition of the baskets of exported goods.
This, in turn, has important consequences for welfare.
Relying on our empirical estimates of transport costs over 1974-2019, we obtain that the 3.7\% reduction of variable costs in Air transport, combined with the reduction in the fixed export costs, has induced an 3.6\% increase in welfare, much higher than if only ad-valorem costs were modeled (2.6\%).
We find a similar result in vessel transport with the observed 4.9\% in total variable costs along with the reduction in the fixed export costs.
The relative increase in welfare is 3.2\% (as compared to 2.8\% in a pure ad-valorem world). Neglecting the existence and long-term evolution additive costs thus leads to a substantial underestimation of the welfare gains of trade cost reduction.
